Formalizing Stack Safety as a Security Property

### 2023-02-02 submission5/intro-v2.tex

Of these mechanisms, many are fundamentally ill-suited for offering formal guarantees,
as they aim to impede attackers but cannot provide universal protection. Shadow stacks,
for instance, aim to ``restrict the flexibility available in creating gadget chains''
\cite{Shanbhogue+19}, not to categorically
rule out attacks. Other mechanisms are stronger, but relatively few formally state their guarantees.
The Cerise work of Skorstengaard et al. \cite{SkorstengaardSTKJFP} and
Georges et al. \cite{Georges22:TempsDesCerises} is so far the sole line of work
to offer (various) stack safety formalizations.

>>>>

Of these mechanisms, many are fundamentally ill-suited for offering formal guarantees,
as they aim to impede attackers but cannot provide universal protection. Shadow stacks,
for instance, aim to ``restrict the flexibility available in creating gadget chains''
\cite{Shanbhogue+19}, not to categorically
rule out attacks. Other mechanisms are stronger, but formal
guarantees are rarely discussed.
Indeed, the Cerise work of Skorstengaard et al. \cite{SkorstengaardSTKJFP} and
Georges et al. \cite{Georges22:TempsDesCerises} is so far the sole line of work
to offer (various)\bcp{Maybe we can omit that word here and spell it
  out in the related work.} stack safety formalizations.
